---
title: "02_merge-clean_data"
author: "Arianna Benedetti"
output: html_document
---
In this code, I will load both datasets into R, merge and clean them, remove observations with non-matching CEOs, remove outliers, and save the datasets for analyses.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
###Install and Load Libraries
install.packages("dplyr", repos="http://cran.rstudio.com/")
library(car)
library(dplyr)
```

## Loading and Merging Datasets

```{r setting up data}

###Load Data###
CEO.pay <-read.csv("~/Box Sync/Berkeley/Fall 2016/PolSci239T/PS239T-final-project/Data/01_glassdoor_ceo_pay.csv", header=T) #previously downloaded CEO pay data
CEO.ratings <-read.csv("~/Box Sync/Berkeley/Fall 2016/PolSci239T/PS239T-final-project/Data/02_glassdoor_ratings.csv", header=T) #dataset from Glassdoor Ratings API

#Join datasets
CEO <- dplyr::inner_join(CEO.pay, CEO.ratings, by = "id")
CEO <- CEO[c("id", "company", "industry", "ceo2015", "ceo2016", "ceo_comp", "median_comp",
             "ratio", "numberOfRatings", "ceoratings", "overall_2014", "overall", "culturevalues",              "wlb", "careerops", "comp", "srleadership", "ceopctApprove", "rectofriend", "profits",                 "size")]

```

# Cleaning Data

## Major cleaning includes:

-Removing all CEOs that do not match b/t 2015 dataset (CEO.pay) and 2016 dataset (CEO.ratings). The CEO-to-worker compensation ratio is my primary predictor variable of interest, and lacks meaning if the CEOs have changed in the time frame between collecting the ratio information and collecting the company ratings information.

-Removing any CEO-to-worker ratio outliers

```{r clean data}

CEO$ceo.match <- NULL
for(i in 1:nrow(CEO)) {
  index <- with(CEO, adist(ceo2015[i], ceo2016[i]))
  CEO$ceo.match[i] <- ifelse(index<=8, "match", "no_match")
}
#Did this work?

non.matches <- CEO[CEO$ceo.match=="no_match",c("company", "ceo2015", "ceo2016", "ceo.match")]
non.matches[1:15,]
matches <- CEO[CEO$ceo.match=="match",c("company", "ceo2015", "ceo2016", "ceo.match")]
matches[1:15,]

#not a perfect comparison, but all matches are correct
#all the incorrect ones appear to be false rejections, so I manually made note of them

#Now, fixing the non_matches that are actually matches
CEO$ceo.match <- as.factor(CEO$ceo.match)
summary(CEO$ceo.match)

#all the wrong ones
CEO$company[c(12, 21, 98, 140, 198, 199, 224, 250, 280, 293, 294, 373, 375, 414, 433)]
CEO$ceo.match[c(12, 21, 98, 140, 198, 199, 224, 250, 280, 293, 294, 373, 375, 414, 433)]
length(CEO$company[c(12, 21, 98, 140, 198, 199, 224, 250, 280, 293, 294, 373, 375, 414, 433)])#15
no.match.replace <- array("match", 15)
#replacing with "match"
CEO$ceo.match[c(12, 21, 98, 140, 198, 199, 224, 250, 280, 293, 294, 373, 375, 414, 433)] <- no.match.replace
CEO$ceo.match[c(12, 21, 98, 140, 198, 199, 224, 250, 280, 293, 294, 373, 375, 414, 433)] 
#now all incorrect non-matches are listed as a match
summary(CEO$ceo.match)


#Make final set with
CEO.analyze <- CEO[CEO$ceo.match=="match",]

#check for outliers in ratio
with(CEO.analyze, plot(CEO.analyze$ratio)) #one big one up near 2000
which(CEO.analyze$ratio>=1500) #this is the index # for that outlier
CEO.outliers <- CEO.analyze #Save the dataset w/outliers for graphing before I make the change to remove the outliers for analyses
CEO.analyze <- CEO.analyze[-which(CEO.analyze$ratio>=1500),] #removing that outlier

#Save the datasets
write.csv(CEO.outliers, "~/Box Sync/Berkeley/Fall 2016/PolSci239T/PS239T-final-project/Data/03_CEO_outliers.csv")
write.csv(CEO.analyze, "~/Box Sync/Berkeley/Fall 2016/PolSci239T/PS239T-final-project/Data/04_CEO_analyze.csv")

#Final count
nrow(CEO.analyze)
nrow(CEO.outliers)
```